### 2023-12-21 documentation/thesis/thesis_document.tex
more thesis

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register your custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor {}
{
public:
    CustomSensor();
    ~CustomSensor();
    // implement depending sensor communication interface
    bool begin(TwoWire& _wire_instance); // I2C
    bool begin(HardwareSerial& _serial_instance); // UART
    bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
    // FUNCTIONS USED BY READOUT LOGIC
    bool is_valid() override;
    String capabilities() override;
    String get_sensor_name() override;
    bool query_sensor() override;
    sensor_result get_result() override;        
};
#endif
\end{lstlisting}

@@

Now that the setup process is complete, the system switches to an
infinite loop, which processes several possible actions. One task is, to
react to user commands which can be sent to the system by the user via
the integrated \gls{cli}. All sensors are read out via a timer interval
set in the setup procedure and their values are stored in a ringbuffer.
Ring buffers, offer efficient data management in limited memory. Its
cyclic structure enables continuous overwriting of older data, saves
memory space and facilitates seamless processing of real-time data. Ring
buffers are well suited for applications with variable data rates and
minimise the need for complex memory management. The buffer can be read
out by command and the result of the measurement is sent to the host.

>>>>

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register your custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor
{
public:
    CustomSensor();
    ~CustomSensor();
    // implement depending sensor communication interface
    bool begin(TwoWire& _wire_instance); // I2C
    bool begin(HardwareSerial& _serial_instance); // UART
    bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
    // FUNCTIONS USED BY READOUT LOGIC
    bool is_valid() override;
    String capabilities() override;
    String get_sensor_name() override;
    bool query_sensor() override;
    sensor_result get_result() override;        
};
#endif
\end{lstlisting}

@@

Now that the setup process is complete, the system switches to an
infinite loop, which processes several possible actions. One task is, to
react to user commands which can be sent to the system by the user via
the integrated \gls{cli}. All sensors are read out via a timer interval
set in the setup procedure and their values are stored in a ringbuffer.
Ring buffers, offer efficient data management in limited memory. Its
cyclic structure enables continuous overwriting of older data, saves
memory space and facilitates seamless processing of real-time data. Ring
buffers are well suited for applications with variable data rates and
minimise the need for complex memory management. The buffer can be read
out by command and the result of the measurement is sent to the host.
Each sensor measurement result is transmitted from the buffer to the
host together with a time stamp and a sequential number. This ensures
that in a multi-sensor setup with several sensors. The measurements are
synchronized\ref{sensor-syncronsisation-interface} in time and are not
out of sequence or drift.
